Supplementary Figures

### 2019-12-20 Supplementary_figures.Rmd
Add highly perturbing elements to supp figure

>>>>

## Highly effective perturbing elements in network

![Interactions of genes that have high perturbation efficiency. Critical gene, represents crucial genes for breast cancer,provided by eDGAR; TFs, transcription factors;  Regulated by TFs, regulated genes with these transcription factors; Physical interaction with critical genes; shared genes in physical interactions between critical genes ](highly_effective_genes.png){#figs10}
